Performance of Rookie Can Predict Price of Their Rookie Prizm Silver Cards

### 2024-04-24 paper/paper.qmd
saved paper
fixed rendering issue

---
title: "Performance of Rookie Can Predict Price of Their Rookie Prizm Silver Cards"
subtitle: "My subtitle if needed"
author: 
  - Harrison Huang
thanks: "Code and data are available at: https://github.com/lemonface88/NBA"
date: today 
date-format: long
abstract: "Collecting and investing in cards has been relevant for a while now. There are complex factors that contribute to the price fluxation of these cards. This analysis will use player statistics to create a model to try to grasp possible future price trends of the card. A linear model was used in this analysis. The results indicated that player statistics may still not be sufficient to predict future prices of the rookie card."
format: pdf
number-sections: true
bibliography: references.bib
---
```{r}
#library(readr)
#write_bib()
```

```{r}
#| include: false
#| warning: false
#| message: false

@@

@@

@@

head(anthony_edward, padding = 5)
```

@@

head(anthony_edward, padding = 5)
```

@@

head(anthony_edward, padding = 5)
```

@@

head(price_data, padding = 5)
```

@@

view(haliburton_prediction_table)
```

@@

kable(haliburton_prediction_table, padding = 5)

@@

```{r}
library(rstanarm)

>>>>

---
title: "Performance of Rookie Can Predict Price of Their Rookie Prizm Silver Cards"
subtitle: "My subtitle if needed"
author: 
  - Harrison Huang
thanks: "Code and data are available at: https://github.com/lemonface88/NBA"
date: today 
date-format: long
abstract: "Collecting and investing in cards has been relevant for a while now. There are complex factors that contribute to the price fluxation of these cards. This analysis will use player statistics to create a model to try to grasp possible future price trends of the card. A linear model was used in this analysis. The results indicated that player statistics may still not be sufficient to predict future prices of the rookie card."
format: pdf
number-sections: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false

@@

library(readr)
#write_bib()

@@

maxey_and_price = read_csv(
  file = "/Users/harrison/NBA/data/analysis_data/maxey_and_price.csv",
  show_col_types = FALSE
)

haliburton_and_price = read_csv(
  file = "/Users/harrison/NBA/data/analysis_data/haliburton_and_price.csv",
  show_col_types = FALSE
)

anthony_and_price = read_csv(
  file = "/Users/harrison/NBA/data/analysis_data/anthony_and_price.csv",
  show_col_types = FALSE
)

@@

kable(anthony_edward, padding = 5)
```

@@

kable(maxey, padding = 5)
```

@@

kable(haliburton, padding = 5)
```

@@

kable(price_data, padding = 5)
```

@@

@@

kable(haliburton_prediction_table, padding = 5)
```

@@

```{r}
#| include: true
#| eval: true
#| echo: false
#| message: false
#| warning: false

pp_check(maxey_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(maxey_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
